### 2018-05-21 Maths Notes/Core/C1/C1.tex
Recurrence relation C1

\begin{document}
\begin{center}
\underline{\huge C1}
\end{center}
\section{Algebra and functions}
\subsection{Indices}
$a^m\times a^n=a^{m+n}$\\
$a^m\div a^n=a^{m-n}$\\
$(a^m)^n=a^{mn}$\\
$a^{-m}=\frac{1}{a^m}$\\
$a^{\frac{1}{m}}=\sqrt[m]{a}$\\
$a^{\frac{n}{m}}=\sqrt[m]{a^n}$\\
\section{Quadratic functions}
\subsection{Discriminant}
\begin{itemize}
\item $b^2>4ac$, Two real solutions
\item $b^2=4ac$, One repeated real solution
\item $b^2<4ac$, No real solution
\end{itemize}
\section{Sketching curves}
\subsection{Graph transformations}
\begin{itemize}
\item f(x)+a, $y$ coordinates increased by a
\item af(x), $y$ coordinates multiplied by a
\item -f(x), reflection in the $x$ axis
\item f(x+a), $x$ coordinates reduced by a
\item f(ax), $x$ coordinates divided by a
\item f(-x), reflection in the $y$ axis
\end{itemize}
\section{Coordinate geometry}
If two lines are perpendicular, the product of their gradients is -1.
\section{Sequences and series}
\subsection{Deriving the formula for the sum of an arithmetic series}
$$S_n=a+(a+d)+(a+2d)+...+(a+(n-1)d)$$
Reverse the sun
$$S_n=(a+(n-1)d)+(a+(n-2)d)+a(a+(n-3)d)+...+(a+d)+a$$
Add the two sums
$$2S_n=[2a+(n-1)d]+[2a+(n-1)d]+[2a+(n-1)d]+...+[2a+(n-1)d]$$
$$2S_n=n[2a+(n-1)d]$$
$$S_n=\frac{n}{2}[2a+(n-1)d]$$

>>>>

\begin{document}
\begin{center}
\underline{\huge C1}
\end{center}
\section{Algebra and functions}
\subsection{Indices}
$a^m\times a^n=a^{m+n}$\\
$a^m\div a^n=a^{m-n}$\\
$(a^m)^n=a^{mn}$\\
$a^{-m}=\frac{1}{a^m}$\\
$a^{\frac{1}{m}}=\sqrt[m]{a}$\\
$a^{\frac{n}{m}}=\sqrt[m]{a^n}$\\
\section{Quadratic functions}
\subsection{Discriminant}
\begin{itemize}
\item $b^2>4ac$, Two real solutions
\item $b^2=4ac$, One repeated real solution
\item $b^2<4ac$, No real solution
\end{itemize}
\section{Sketching curves}
\subsection{Graph transformations}
\begin{itemize}
\item f(x)+a, $y$ coordinates increased by a
\item af(x), $y$ coordinates multiplied by a
\item -f(x), reflection in the $x$ axis
\item f(x+a), $x$ coordinates reduced by a
\item f(ax), $x$ coordinates divided by a
\item f(-x), reflection in the $y$ axis
\end{itemize}
\section{Coordinate geometry}
If two lines are perpendicular, the product of their gradients is -1.
\section{Sequences and series}
\subsection{Deriving the formula for the sum of an arithmetic series}
$$S_n=a+(a+d)+(a+2d)+...+(a+(n-1)d)$$
Reverse the sun
$$S_n=(a+(n-1)d)+(a+(n-2)d)+a(a+(n-3)d)+...+(a+d)+a$$
Add the two sums
$$2S_n=[2a+(n-1)d]+[2a+(n-1)d]+[2a+(n-1)d]+...+[2a+(n-1)d]$$
$$2S_n=n[2a+(n-1)d]$$
$$S_n=\frac{n}{2}[2a+(n-1)d]$$
\subsection{Forming a recurrence relation}
To create a recurrence relation formula from a formula given in n, substitute n+1 in place of n and rearrange.\\
\textbf{Example}
$$U_n=2^n+4n$$
$$U_{n+1}=2^{n+1}+4{n+1}$$
$$U_{n+1}=2U_n-4n+4$$
\subsection{Finding a and d}
Remember that the formula for the $\textrm{n}^\textrm{th}$ term may not be given in the form $a+(n-1)d$, and if it is not, it must be changed.\\
\textbf{Example}\\
$u_r=4r-7$\\
$u_1=4-7=-3=a$\\
$4r-7=-3+(r-1)d \quad \Rightarrow 4r-4=(r-1)d \quad \Rightarrow d=4$
\subsection{Finding the nth term from a recurrence relation}
To find the nth term, use a standard form, deducted from what is happening to the previous term.\\
\textbf{Example}\\
$U_{n+1}=2U_n-5$\\
The multiplier by 2 implies doubling, and so the nth term will contain $A\times2^n$, the subtraction of 5 suggests there will also be a constant term, $B$.\\
$$U_n=A\times2^n+B$$
Given $U_1=6$, A and B can be found to be $\frac{1}{2}$ and 5.

### 2018-05-21 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex

@@

\section{Hypothesis tests for PMCC and Spearman's Rank Correlation Coefficient}
Spearman's rank - The tendency for y to increase as x increases\\
PMCC - How close x and y are to a linear relationship\\
Spearman's rank is equivalent to PMCC if the data is ranked, this causes the data to adopt a linear relationship if y increases as x increases.\\
The Spearman's rank formula does not work if there are tied ranks\\
The critical values in the PMCC table assume that the data is jointly normally distributed, this is the assumption if asked for a hypothesis test. The spearman's rank distribution doesn't assume the data to be jointly normally distributed.\\
$\rho$ is the population parameter which is the \textbf{actual} correlation between the variables.\\
$r$ and $r_s$ is the observed correlation based on the sample\\
Hypothesis tests can be either one or two tailed, depending if you are just looking for a correlation or specifically a positive/negative correlation.

>>>>

\subsubsection{Continuous uniform distribution}
Remember when testing for a uniform distribution to state that it is a \textbf{continuous} uniform distribution

@@

Contingency tables and PMCC tests both look for linear relationships, however a contingency table looks to see if the data lies on the line $y=x$, whereas the PMCC looks to see if the data lies on the line $y=kx$

\section{Hypothesis tests for PMCC and Spearman's Rank Correlation Coefficient}
Spearman's rank - The tendency for y to increase as x increases\\
PMCC - How close x and y are to a linear relationship\\
\\
Spearman's rank is equivalent to PMCC if the data is ranked, this causes the data to adopt a linear relationship if y increases as x increases.\\
\\
The Spearman's rank formula does not work if there are tied ranks\\
\\
The critical values in the PMCC table assume that the data is jointly normally distributed, this is the assumption if asked for a hypothesis test. The spearman's rank distribution doesn't assume the data to be jointly normally distributed.\\
\\
$\rho$ is the population parameter which is the \textbf{actual} correlation between the variables.\\
$r$ and $r_s$ is the observed correlation based on the sample\\
\\
Hypothesis tests can be either one or two tailed, depending if you are just looking for a correlation or specifically a positive/negative correlation.
\newpage
\begin{center}
\underline{\huge Hypothesis tests}
\end{center}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{What is being tested}&$\mathbf{H_0}$&$\mathbf{H_1}$\\
\hline
Difference between means&$\mu_a=\mu_b$&$H_1:\mu_a>\mu_b \ \textrm{or} \ 
\mu_a<\mu_b \  \textrm{or} \ 
\mu_a\neq\mu_b$\\
\hline
Goodness of fit&A \underline{\hspace{1cm}} Distribution is a suitable model&A \underline{\hspace{1cm}} Distribution is not a suitable model\\
\hline
Contingency Tables&No association between the two data sets&Association between the two data sets\\
\hline
Spearman's rank&$\rho_s=0$&$\rho_s>0,\rho_s<0,\rho_s\neq0$\\
\hline
PMCC&$\rho=0$&$\rho>0,\rho<0,\rho\neq0$\\
\hline
\end{tabularx}
\begin{center}
\underline{\huge Tables}
\end{center}
\setcounter{section}{6}
\subsection{Goodness of fit}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
Number&&\\
\hline
Observed&&\\
\hline
Expected&&\\
\hline
$\dfrac{(O-E)^2}{E}$&&\\
\hline
\end{tabularx}}
\subsection{Contingency tables}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
\hline
&\multicolumn{3}{|c|}{\centering C}&\multicolumn{3}{|c|}{\centering D}\\
\cline{2-7}
&O&E&$\frac{(O-E)^2}{E}$&O&E&$\frac{(O-E)^2}{E}$\\
\hline
A&&&&&&\\
\hline
B&&&&&&\\
\hline
\end{tabularx}}
\subsection{Difference between means}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
&A&B\\
\hline
$\overline{x}$&&\\
\hline
$s^2$&&\\
\hline
n&&\\
\hline
\end{tabularx}
\subsection{Spearman's rank}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
&A&B&C\\
\hline
Rank 1&&&\\
\hline
Rank 2&&&\\
\hline
$d^2$&&&\\
\hline

\end{tabularx}

### 2018-05-21 Test/Definitions/Definitions.tex
Update of all files to shorten preamble
Tidied to work with all linux systems

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - S3}

\begin{document}
\begin{center}
\underline{\huge Definitions}
\end{center}
\large
Hypothesis - A statement concerning a population parameter\\
Critical Region - The range of values that would lead to the rejection of $H_0$, and so the acceptance of $H_1$\\
Statistic - A random variable, a function of known observations from a population, no unknown parameters\\
Sampling unit - An individual unit of the population\\
Sampling frame - A list of all sampling units\\
Sampling distribution - All possible samples are chosen from the population\\
Census - When every member of the population is investigated\\
Hypothesis test - A mathematical procedure to examine a value of
a population parameter proposed by the null hypothesis compared with an alternative hypothesis\\
Population - A collection of all items\\
Finite Population - One in which each individual member can be given a number\\
Infinite population - One where it is impossible to number each individual member\\
Significance level - The probability of incorrectly rejecting $H_0$\\
Sample - A selection of items from a population\\

\end{document}

>>>>

\documentclass{article}
\usepackage[a4paper,hmargin=3cm,vmargin=5cm]{geometry}
\usepackage{pdflscape,lipsum,graphicx}
\usepackage[absolute]{textpos}
\usepackage{fancyhdr}
\usepackage{afterpage}

\begin{document}
Test
\newpage

\newgeometry{landscape}     % use whatever margins you want for left, right, top and bottom.
...
... %<The contents of enlarged page(s)>
...    
\restoregeometry     %so it does not affect the rest of the pages.
\end{document}
